Fisher vector places: learning compact image descriptors for place recognition

### 2014-11-10 cvpr15review.tex
minor changes

%%%%%%%%% TITLE
\title{\LaTeX\ Fisher vector places: learning compact image descriptors for place recognition}

@@

   \paragraph{Analysis of per-exemplar SVM objective} %\vspace{-0.2cm} 
      In this section, we analyze the exemplar SVM objective~(\ref{eq:obj}) and show the learnt and {\em re-normalized} weight vector $w_j$ can be interpreted as a new descriptor $\Psi_j$ that replaces the original positive training descriptor $\Phi^+_j$.  In particular, we show first that when the weight $C_2$ of the negative data in objective~(\ref{eq:obj}) goes to zero and the learnt $\Psi_j$ is identical to the original positive training data point $\Phi_j^+$.  Second, when $C_2>0$, the learnt $\Psi_j$ moves away from the positive $\Phi_j^+$ to increase its separation from the negative data.
      Details are given next.

@@

   \paragraph{Interpreting normalized $w$ as a new descriptor} %\vspace{-0.2cm} 
      The above analysis demonstrates that as $C_2$ decreases the normal of the optimal hyperplane $w$ that separates the positive exemplar $\Phi^+$ from negative data becomes parallel with $\Phi^+$, as shown in figure \ref{fig:C2effect}. As $C_2$ increases, the normal $w$ of the optimal hyper-plane moves away from the direction given by the positive example $\Phi^+$ in a manner that reduces the loss on the negative data. 
      This suggests that the learnt $w$ could be interpreted as a modified positive example $\Phi^+$, re-weighted to emphasize directions that separate $\Phi^+$ from the negative data. As discussed above $w$ is not normalized. As we wish to measure the similarity between descriptors by (the cosine of) their angle        
      given by equation \eqref{eq:class}, additional normalization of the learnt $w$ is necessary. Hence we define the new descriptor $\Psi_j$ as the normalized hyperplane normal $w_j$
         %
         \begin{equation}
            \label{eq:normalization}
            \Psi_j=\dfrac{w_j}{||w_j||}.
         \end{equation}

>>>>

%%%%%%%%% TITLE
\title{Fisher vector places: learning compact image descriptors for place recognition}

@@

   \subsection{Analysis of per-exemplar SVM objective} %\vspace{-0.2cm} 
      In this section, we analyze the exemplar SVM objective~(\ref{eq:obj}) and show the learnt and {\em re-normalized} weight vector $w_j$ can be interpreted as a new descriptor $\Psi_j$ that replaces the original positive training descriptor $\Phi^+_j$.  In particular, we show first that when the weight $C_2$ of the negative data in objective~(\ref{eq:obj}) goes to zero and the learnt $\Psi_j$ is identical to the original positive training data point $\Phi_j^+$.  Second, when $C_2>0$, the learnt $\Psi_j$ moves away from the positive $\Phi_j^+$ to increase its separation from the negative data.
      Details are given next.

@@

   \subsection{Interpreting normalized $w$ as a new descriptor} %\vspace{-0.2cm} 
      The above analysis demonstrates that as $C_2$ decreases the normal of the optimal hyperplane $w$ that separates the positive exemplar $\Phi^+$ from negative data becomes parallel with $\Phi^+$, as shown in figure \ref{fig:C2effect}. As $C_2$ increases, the normal $w$ of the optimal hyper-plane moves away from the direction given by the positive example $\Phi^+$ in a manner that reduces the loss on the negative data. 
      This suggests that the learnt $w$ could be interpreted as a modified positive example $\Phi^+$, re-weighted to emphasize directions that separate $\Phi^+$ from the negative data. As discussed above $w$ is not normalized. As we wish to measure the similarity between descriptors by (the cosine of) their angle        
      given by equation \eqref{eq:class}, additional normalization of the learnt $w$ is necessary. Hence we define the new descriptor $\Psi_j$ as the normalized hyperplane normal $w_j$
         %
         \begin{equation}
            \label{eq:normalization}
            \Psi_j=\dfrac{w_j}{||w_j||}.
         \end{equation}
